Interpersonal Accuracy of Thoughts, Affect, and Personality Traits

### 2022-05-24 manuscript.Rmd
EK Peer Review
Peer Review for EDLD 653

```{r, include = FALSE}
# import functions
source("functions.R") # good idea to source functions here~

@@

>>>>

```{r, include = FALSE}
# import functions
source("functions.R")

@@

###EK Peer Review

#Strengths
1. Reproducibility is great! Having some knitting issues with the model dyad portion, but overall the functions file and structure of the tidying and analysis are easy to follow.
2. Using functional programming all over the place! The walk2 at the beginning of the results section is particularly nice.
3. I don't fully understand the data or analyses that were run here, however the thorough comments were enough to get me the gist, as well as understand the functions I was not familiar with yet.

One thing I learned: use of the rm function to clean the environment, that might be helpful if you were having memory issues with the r environment.

One area that could be improved: very small, could write a wrapper function for lmer that allows you to pass the data, left side formula value, and numerator to use on the right side.
